Traffic Analysis of Large File Downloads on Tor

### 2017-05-08 paper.tex
Added section for results and conclusion - I am going to bed now...
add abstract, proofread, add some results

\documentclass[12pt,journal]{IEEEtran}
\usepackage[
  backend=biber,
  style=numeric,
  citestyle=numeric
]{biblatex}
\usepackage{graphicx}
\addbibresource{citations.bib}
\providecommand{\keywords}[1]{\textbf{Keywords} #1}
\begin{document}
\title{Traffic Analysis on Tor}
\author{\IEEEauthorblockN{William Liddy\IEEEauthorrefmark{1}, Brian Pollack\IEEEauthorrefmark{2}}\\
        \IEEEauthorblockA{Department of Electrical Engineering and Computer Science\\Case Western Reserve University\\Cleveland, OH 44106\\\IEEEauthorrefmark{1}wjl36@case.edu, \IEEEauthorrefmark{2}bmp55@case.edu}}
\maketitle

\begin{abstract}
TODO: Abstract
\end{abstract}

@@

\section{Introduction}
\IEEEPARstart{T}{his} is the introduction.

\section{Background}
\subsection{Tor Architecture}
Tor is a circuit-based anonymous communication service that uses Onion Routing to securely pass packets in the network.
\par
A Tor circuit is the path that communication takes from the client to the desired destination. A circuit consists of multiple servers, called nodes, and is typically three nodes, or hops, long. To set up a circuit, the client must know the servers in which it would like to connect. The Tor network provides a list of appropriate nodes. The client then can send TCP packets through the circuit.
\par
Onion Routing is an overlay network protocol that is designed to carry TCP packets over existing networks. Traffic flows through the network in fixed size segments. Each node unwraps a layer from the packet using a symmetric key and forwards it to the next node. The packet is unwrapped like an union, which is where the name comes from.
\par
Tor routes its traffic using circuits. A user will set up a circuit using at least three Tor nodes, and that circuit stays active until the user either is finished or requests a new circuit. Tor circuits can carry any TCP packet, as long as the application supports routing through Tor, however cannot carry UDP packets. A single Tor circuit can carry multiple simultaneous streams, which is good for HTTP traffic which opens multiple connections to multiple destinations.
\par
One common attack against anonymous communication networks is known as traffic analysis. An attacker will analyze the traffic through a network to try to de-anonymize the users.
\par
While some anonymity services will reorder, mix, or otherwise shape the traffic flowing between Onion Routers, Tor chooses to not attempt to shape the traffic. The creators believed that all currently available traffic shaping strategies were still vulnerable to attacks and were difficult to implement practically. They also wanted to make Tor as low-latency as possible, and reordering packets would increase latency. Tor simply sends traffic in a round robin fashion.
\par
To protect against traffic bottlenecks, Tor uses a decentralized congestion control mechanism that sends end-to-end ack packets to maintain anonymity while allowing edge nodes to detect congestion and throttle their traffic until congestion subsides.
\par
Traffic is only allowed to leave the Tor network through nodes which specifically allow exits (called exit nodes). Each node has a policy stating which traffic is allowed to leave the network: this can be restricted by IP address or protocol. \cite{Dingledine:2004:TSO:1251375.1251396}

@@

If an attacker could identify individual users, this would constitute a major problem for Tor. If the entire point is to keep users anonymous, and it is proven that it is possible to de-anonymize certain users, the Tor network has significant problems that need to be addressed.

@@

Tor is designed to protect against an adversary who can observe some fraction of network traffic. This adversary can generate, modify, delete, or delay traffic and can operate his or her own tor nodes. The adversary can also compromise some fraction of existing tor nodes\cite{Dingledine:2004:TSO:1251375.1251396}.

@@

Additionally, it is important to note that Tor does not protect against traffic confirmation attacks, which are when an adversary suspects two parties are communicating and tries to prove it by analyzing the network. Tor rather attempts to make it difficult to identify who is communicating without a solid suspicion \cite{Murdoch:2005:LTA:1058433.1059390}.

@@

With our attacks, we try to gain information about the path of the Tor circuit using methods available to all Tor users. It is important to note that we do not exit the threat model for which Tor is built. We demonstrate that small attackers are able to gain insights about Tor users. This means that both government and non-government agencies are able to carry out these attacks on Tor.

@@

Traffic analysis is the process of observing data from a network and making assumptions about users based on numerous properties such as the timing of packets or header information such as source and destination IP addresses. In the scope of anonymous networks, traffic analysis can be used with the goal of identifying end-users who are trying to remain anonymous \cite{Murdoch:2005:LTA:1058433.1059390}.

@@

Traffic analysis can be performed on the packets traveling through the Tor network. The attacker will not be able to read the header information or content of the original TCP packets because they are encased in the onion routing packets, but an attacker is able to gain information based on those onion routing packets.

@@

Traffic analysis can be performed in multiple ways. An attacker can directly observe packets if he or she controls part of the network where the packets are flowing. Alternatively, an attacker can indirectly gain insights on a server by using measurements such as round trip time or a measurement of throughput on data through the server.

@@

We believe that if an attacker is observing a subset of nodes, he or she is able to effectively identify end-users through traffic analysis. Because we do not require a global observation of the network and do not require many Tor nodes under the attacker’s control, our network analysis attack is within the Tor threat model.

@@

In 2005, Murdoch and Danezis studied similar attacks to the Tor network. They assumed that an adversary created a corrupt Tor node on the network. The corrupt node is then used to measure other nodes' traffic load. Additionally, they assumed that the attackers controlled a network server that the user to be traced is accessing. Murdoch and Danezis claim that this threat is within the threat model that should be covered by Tor. If the attackers modulate the data through the network server that the user is accessing, they were able to observe similar modulations in the Tor circuit that the user was using. This means, therefore, that the attackers could trace the user through the Tor circuit and link a user with the services he or she is using \cite{Murdoch:2005:LTA:1058433.1059390}. Figure \ref{murdochsetup} shows Murdoch and Danezis's attack setup.

@@

Because Murdoch and Danezis were able to observe the change in traffic patterns as users connected to a web service through a Tor circuit, they could infer which nodes were part of that circuit. This information by itself, however, does not seem too useful. At face value, we have identified servers through which a user is using to mask his or her traffic, but have not yet found that user. If we are the government or otherwise have access to the user's ISP, we can request logs of who is communicating with the servers in the Tor circuit and therefore can most likely identify the exact user who is trying to remain anonymous. This is disastrous in countries where the users are trying to remain anonymous due to government censorship as the government likely has access to this information.

@@

We wanted to test to see if the Tor network was still vulnerable to Murdoch and Danezis's attack. We did not simply duplicate their attack. Rather, we modified it slightly and reevaluated the exact attack scenarios. We wanted to demonstrate that this attack has significant real world implications that need to be addressed by the Tor network.

@@

If anybody could immediately add a node to the Tor network and advertise that it can handle a large amount of traffic, other users would immediately start sending data through that new node. This means that an adversary could easily set up a node and allow many clients to set up circuits through it, then delay or drop those connections. It would be easy for adversaries to disrupt the Tor network. To combat this issue, Tor uses a measurement called consensus weight. Each client starts with a low consensus weight and, as other users send data through the new node, if the Tor network determines that the new node is performing well, the consensus weight will increase. The Tor network sends more traffic to nodes with a higher consensus weight.

@@

To configure the Tor service on a unix machine, the node operator has to modify the torrc configuration file. We just talked about the Tor service automatically ramping up bandwidth, but we point out that a node operator may choose to force the node to use a smaller bandwidth than his or her network will allow. An operator may choose to restrict bandwidth so the Tor node does not consume too much of the network.

@@

It is also worth stating that there are many other configuration options for the Tor service, and they are mostly located in the torrc configuration file. An operator can choose whether or not to allow the node to operate as a relay node or as an exit node and can set the ports that the tor service uses, among many other configuration options.

@@

We begin with the assumption that a client will be accessing a service over the Tor network. We can also assume that an attacker has some control over and can generate, modify, delete, or delay traffic on either the client's network or the network of the web service. Lastly, we assume that the attacker has the ability to add a few nodes to the Tor network. All three of these assumptions are within the Tor threat model \cite{Dingledine:2004:TSO:1251375.1251396}.
To conduct our experiments, we first set up one Tor relay node and one Tor exit node, both using Lightsail on Amazon Web Services, and waited for them to be accepted to the Tor network.
\subsubsection{Our Victim}We then set up a victim machine which used the Tor network to download a large photo. The photo was hosted on an Apache webserver on the same machine as the victim client. The victim client used the Tor network to reach an arbitrary exit node which would then connect back to the webserver and download the image. The victim client was programmed to download the image for sixty seconds, then pause for sixty seconds, then repeat this process with a new Tor circuit.
\subsubsection{Our Analysis Node}The victim machine sent the fingerprints of the Tor nodes in each circuit it was using to our analysis node. The analysis node set up a Tor circuit through one of the nodes in the victim's circuit so it could try to detect that the client was using that node. We measured both the change in RTT and change in throughput through the analyzed node. See figure \ref{oursetup} for a diagram of our setup.
\subsubsection{Implications}
This setup is not unreasonable. We had three machines involved, including both the victim and analysis nodes. If the attacker has access to a victim's network, he or she could modulate the traffic by delaying packets, causing similar delays that we were using to experiment. If the attacker has access to the server to which the victim is connecting, the attacker can modulate the traffic there.
One additional way, which is the easiest for attackers to exploit, is for an attacker to interject his or her own content into the victim's connection by serving his or her modulated content on a legitimate website that the victim is accessing. For example, the simplest way of forcing the victim to download this modulated traffic is if the attacker purchased an advertisement on a website the victim was browsing. The attacker could then modulate the content that is downloaded by the client to load the advertisement.
Next, the attacker would need to have enough analysis nodes to be able to measure a significant percentage of the available Tor nodes. Because the attacker does not know any information about the victim's Tor circuit, he or she will need to analyze multiple nodes until the circuit is discovered. Especially if the search was limited to a subset of the active Tor nodes, we believe it is not unreasonable to assume that this attack is possible. The subset of measured nodes could start with all of the guard nodes, for example, which we know should constitute one hop in the victim's circuit.

\printbibliography
\end{document}

>>>>

\documentclass[12pt,journal]{IEEEtran}
\usepackage[
  backend=biber,
  style=numeric,
  citestyle=numeric
]{biblatex}
\usepackage{graphicx}
\addbibresource{citations.bib}
\providecommand{\keywords}[1]{\textbf{Keywords} #1}
\begin{document}
\title{Traffic Analysis of Large File Downloads on Tor}
\author{\IEEEauthorblockN{William Liddy\IEEEauthorrefmark{1}, Brian Pollack\IEEEauthorrefmark{2}}\\
        \IEEEauthorblockA{Department of Electrical Engineering and Computer Science\\Case Western Reserve University\\Cleveland, OH 44106\\\IEEEauthorrefmark{1}wjl36@case.edu, \IEEEauthorrefmark{2}bmp55@case.edu}}
\maketitle

\begin{abstract}
Tor is a popular anonymity network used by millions to access internet services while maintaing their privacy. The main idea behind Tor is that clients build a "circuit" of relays, where each relay carries traffic to the next relay, without any single relay knowing the full extent of the path. Thus, anoynmity is acheived, becuase no relay can trace the client to the destination.

However, A paper written in 2005 titled "Low-Cost Traffic Analysis of Tor" by Steven J. Murdoch and George Danezis demonstrated that a traffic analysis attack was possible against the Tor network. Any attacker could monitor the load on a relay in the Tor network by calculating the RTT to the relay, and when the RTT spiked, it was clear that the relay was being used. With this information, attackers could trace the path of a client in the Tor network and de-anonymize them.

This paper was written in 2005, when Tor was still young. At the time of Murdoch and Danezis' paper, the entire Tor network consisted of just fifty relays. As the time of writing, there were well over 7,000 relay relays in the network, so the ecosystem of Tor is radically different. With all of the increased traffic, we wanted to discover if this type of attack was still valid.

Our results indicate that if a victim is downloading a large file as fast as Tor will allow them to, a decrease in bandwidth and an increase in round trip time (RTT) is usually observable on the relay. We also discovered that Tor guard relays, a special subset of relay that clients will pick at the first hop in their circuit, are very susceptible to this kind of attack.

\end{abstract}

@@

\section{Introduction}
\IEEEPARstart{T}{or} 
\section{Background}
\subsection{Tor Architecture}
Tor is a circuit-based anonymous communication service that uses Onion Routing to securely pass packets in the network.
\par
A Tor circuit is the path that communication takes from the client to the desired destination. A circuit consists of multiple servers, called relays, and is typically three hops long. To set up a circuit, the client must know the IP addresses of the three relays of which it would like to build the circuit of. The Tor network provides a list of appropriate relays through a service called a directory authority. The client then can send TCP packets through the circuit.
\par
Onion Routing is an overlay network protocol that is designed to carry TCP packets over a circuit without revealing the path of the circuit to any single relay. To set up an onion-routed circuit, the client starts by encoding the IP address of the destination with the public key of the last relay, then encoding that entire message with the key of the second-to-last relay, and so on. When the first relay recieves the packet to transmit, it "unwraps" a layer from the packet using it's private key and forwards the message to the address of the relay that is revealed. The packet is unwrapped like an union, which is where the name comes from.
\par
Tor routes its traffic using Onion Routing. A user will set up a circuit using at least three Tor relays, and that circuit stays active until the user either is finished or requests a new circuit. Tor circuits can carry any TCP packet, as long as the application supports routing through Tor, however, it cannot carry UDP packets. A single Tor circuit can carry multiple simultaneous streams, which is good for HTTP traffic which opens multiple connections to multiple destinations.
\par
One common attack against anonymous communication networks is known as traffic analysis attack. An attacker will analyze the traffic through a network to try to de-anonymize a user. While some anonymity services will reorder, mix, or otherwise shape the traffic flowing between Onion Routers, Tor chooses to not attempt to shape the traffic. The creators believed that all currently available traffic shaping strategies were still vulnerable to attacks and were difficult to implement practically. They also wanted to make Tor as low-latency as possible, and reordering packets would increase latency.
\par
Furthermore, to protect against traffic bottlenecks, Tor uses a decentralized congestion control mechanism that sends end-to-end ACK packets to maintain anonymity while allowing edge relays to detect congestion and throttle their traffic until congestion subsides.
\par
Traffic is only allowed to leave the Tor network through relays which specifically allow exits (called exit nodes). Each node has a policy stating which traffic is allowed to leave the network: this can be restricted by IP address or protocol. \cite{Dingledine:2004:TSO:1251375.1251396}

@@

If an attacker could identify individual users, this would constitute a major problem for Tor. The entire point of Tor is to keep users anonymous, and if it is proven that it is possible to de-anonymize users, then the Tor network has a significant flaw that needs to be addressed.

@@

Tor is designed to protect against an adversary who can observe some fraction of network traffic. This adversary can generate, modify, delete, or delay traffic and can operate his or her own Tor relays. The adversary can also compromise some fraction of existing Tor relayss\cite{Dingledine:2004:TSO:1251375.1251396}.

@@

Additionally, it is important to note that Tor does not protect against traffic confirmation attacks, which occur when an adversary suspects two parties are communicating and tries to prove it by analyzing the network. Tor rather attempts to make it difficult to identify who is communicating without a solid suspicion \cite{Murdoch:2005:LTA:1058433.1059390}.

@@

With our attack model, we try to gain information about the path of the Tor circuit using methods available to all Tor users. It is important to note that we do not exit the threat model for which Tor is built. We demonstrate that anyone with sufficent know-how and a few Tor relays can potentially deanonymize Tor users- no large investment or "insider" information is needed.

@@

Traffic analysis is the process of observing traffic from a network and making assumptions about users based. Metrics these assumptions use include the timing of packets and header information such as source and destination IP addresses. In the scope of anonymous networks, traffic analysis can be used with the goal of identifying end-users who are trying to remain anonymous \cite{Murdoch:2005:LTA:1058433.1059390}.

@@

Traffic analysis can be performed on the packets traveling through the Tor network. The attacker will not be able to read the header information of the original TCP packets because they are encased in the onion routing packets, but an attacker is able to gain information based on those onion routing packets.

@@

Traffic analysis can be performed in multiple ways. An attacker can directly observe packets if he or she controls part of the network. Alternatively, an attacker can indirectly gain insights on a relay by using measurements such as round trip time (RTT) or a measurement of throughput on the relay.

@@

We believe that if an attacker is observing a subset of relays, he or she is able to effectively identify end-users requesting large amounts of bandwidth through traffic analysis. Because we do not require a global observation of the network and do not require many Tor nodes under the attacker’s control, our network analysis attack is within the Tor threat model.

@@

In 2005, Murdoch and Danezis studied the possibility of network analysis attacks on the Tor network. In their attack model, an adversary created a corrupt Tor relay on the network. The corrupt relay was then used to measure other relays' traffic load by measuring the RTT to that relay. Additionally, they assumed that the attacker controlled a network server that the victim is accessing. Murdoch and Danezis claim that this threat is within the threat model that should be covered by Tor. If the attackers modulate the data through the network server that the user is accessing, they were able to observe similar modulations in the Tor circuit that the user was using. This means, therefore, that the attackers could trace the user through the Tor circuit and link a user with the services he or she is using \cite{Murdoch:2005:LTA:1058433.1059390}. Figure \ref{murdochsetup} shows Murdoch and Danezis's attack setup.

@@

Because Murdoch and Danezis were able to observe the change in traffic patterns as users connected to a web service through a Tor circuit, they could infer which nodes were part of that circuit. This information alone, however, does not seem to be useful. The attacker may have identified servers through which a victim communicated, but have not yet found that victim. If the attacker has access to the user's ISP, then the attacker can get the logs of the IP is communicating with the discovered relays in the Tor circuit and therefore can most likely identify the exact user who is trying to remain anonymous. This makes Tor unsecure for users who have ISPs that are not willing to protect their privacy, such as countries where government controls the ISP in order to censor material.

@@

We wanted to test if the modern Tor network was still vulnerable to Murdoch and Danezis's attack. But we did not duplicate the attack exactly- rather, we modified it slightly and reevaluated the exact attack scenarios. Our attack specifically targets "guard nodes", which are the first nodes in every Tor circuit.

@@

If anybody could immediately add a relay to the Tor network and advertise that it can handle a large amount of traffic, other users would immediately start sending data through that new node. This means that an adversary could easily set up a node and allow many clients to set up circuits through it, then delay or drop those connections. It would be easy for adversaries to disrupt the Tor network. To combat this issue, Tor assigns a measurement to each node called consensus weight. Each client starts with a low consensus weight and, as other users send data through the new node, if the Tor network determines that the new node is performing well, the consensus weight will increase. The Tor network sends more traffic to nodes with a higher consensus weight.

@@

To configure the Tor service, the node operator has to modify the torrc configuration file. We would like to point out that a node operator may choose to force the node to use a smaller bandwidth than his or her network will allow. An operator may choose to restrict bandwidth for a variety of reasons.

@@

It is also worth stating that there are many other configuration options for the Tor service, and they are mostly located in the torrc configuration file. An operator can choose whether or not to allow the node to operate as a relay node or as an exit node and can set the ports that the Tor service uses, among many other configuration options.

@@

We begin with the assumption that a client will be accessing a service over the Tor network (in our case, an HTTP server). We also assume that an attacker has some control over and can generate, modify, delete, or delay traffic on either the client's network or the network of the web service. Lastly, we assume that the attacker has the ability to add a few nodes to the Tor network. All three of these assumptions are within the Tor threat model \cite{Dingledine:2004:TSO:1251375.1251396}.
To simulate the attacker, we first set up one Tor relay and one Tor exit node, both using Lightsail on Amazon Web Services, and waited for them to be accepted to the Tor network.

\subsubsection{Our Victim}We then set up a simulated victim machine which used the Tor network to download a large (1 GB) photo. The photo was hosted on an Apache Webserver on the same machine as the victim. The reason the victim routed to itself was to assure that the Tor network was the bottleneck- not our websever. Additonally, using a public resource might throttle the client or otherwise cause changes in bandwidth during the experiment, which would lead to undesired modulation in the data due to the change the traffic going through the Tor network. The victim client used the Tor network to reach a fixed exit node which would then connect back to the webserver and download the image.

The victim client was programmed accept a list of Tor relay addresses. With this list, the victim client would construct a 2-hop Tor circuit that consisted of the first relay in the list, then the fixed exit node. The victim would then proceed to download the image for sixty seconds, then pause for sixty seconds, then repeat this process with the next relay in the list. This list was also sent to the analysis node, which is covered in the next section.

\begin{figure*}
 \center
  \includegraphics[width=0.4\textwidth]{figures/rtt_guard.png}
  \includegraphics[width=0.4\textwidth]{figures/thr_guard.png}
  \caption{Results of run over 50 high-consensus relays}
  \label{AAA}
\end{figure*}

\begin{figure*}
 \center
  \includegraphics[width=0.4\textwidth]{figures/rtt_avg.png}
  \includegraphics[width=0.4\textwidth]{figures/thr_avg.png}
  \caption{Results of run over 25 random relays. Outliers excluded.}
  \label{AAA}
\end{figure*}

\subsubsection{The Analysis Exit Node} The Analysis exit node has the same list of relays as the vicitim, and since the victim is deterministic in it's timing, the analysis relay knows exactly what node the victim is connected to. The analysis node sets up a Tor circuit through the node the victim is currently connected to. It would measure both the change in RTT and change in throughput (via downloading a large file, with the same setup as the client) through the analyzed node during and after the download. See figure \ref{oursetup} for a diagram of our setup.

\subsubsection{Implications}
This setup is not unreasonable. We had three machines involved, including both the victim and analysis nodes. If the attacker has access to a victim's network, he or she could modulate the traffic by delaying packets, causing similar delays that we were using to experiment. If the attacker has access to the server to which the victim is connecting, the attacker can modulate the traffic there.
One additional way, which is the easiest for attackers to exploit, is for an attacker to interject his or her own content into the victim's connection by serving his or her modulated content on a legitimate website that the victim is accessing. For example, the simplest way of forcing the victim to download this modulated traffic is if the attacker purchased an advertisement on a website the victim was browsing. The attacker could then modulate the content that is downloaded by the client to load the advertisement.
Next, the attacker would need to have enough analysis nodes to be able to measure a significant percentage of the available Tor nodes. Because the attacker does not know any information about the victim's Tor circuit, he or she will need to analyze multiple nodes until the circuit is discovered. Especially if the search was limited to a subset of the active Tor nodes, we believe it is not unreasonable to assume that this attack is possible. The subset of measured nodes could start with all of the guard nodes, for example, which we know should constitute one hop in the victim's circuit.

It should also be noted that in our attack model, we assume the client is downloading a file from Tor as quickly as Tor will allow them to. While this is the same technique that Murdoch's attack uses, it should be noted that traffic analysis attacks such as this one are limited to situations where the victim is obtaining a large amount of data over a long period of time. We acknowledge that this attack will not work against users requesting resources sporadically- such as just viewing HTML pages, and reading them. This attack is still very valid against vicitims who are downloading a large file or streaming content.

\subsection{Our Results}
Firstly, we ran our analysis on the 50 highest-consensus relays in the network. These were made pubically available through a service called Onionoo. The results of the RTT analysis and bandwidth analysis are shown in figure 3.

When the client was downloading a file through one of these relays, the observable RTT increased by 23.5\% compared to when the client was not downloading anything, on average. Of the 50 nodes tested, an increase in RTT was obserable on 49. This means that for an overwhelming majority of high-consensus relays (those likely to be guard nodes), traffic analysis attacks are still very possible given that the client is using a lot of bandwidth.

We also expand on Murdoch's findings by introducing the idea that throughput analysis attacks are viable. When the client was downloading a file through one of these relays, the observable throughput when another Tor user was also downloading a file decreased by -27.2\% compared to when the client was not downloading anything, on average. Of the 50 nodes tested, an decrease in throughput was obserable on 43 of the relays. While not as sure-fire as the RTT for traffic analysis, most relays are still susceptible to this kind of analysis.

We also ran our analysis on 50 randomly selected relays from the Tor network. Many of these relays acted erratically, and we would regularly see connections dropped, and RTTs and throughput go to zero in the middle of a run. Of the 33 nodes that had successful runs, we removed the 4 highest and 4 lowest outliers for a total of 25 nodes. This is shown in figure 4.

\section{Conclusions}
TODO
\printbibliography
\end{document}
